% Thanks be to James Bennett.

Firstly, I would like to thank my supervisor Majid Ezzati for his guidance and mentorship.
I have learnt so much from you over the past years, and it's inspiring to see the level of care and attention you pay towards your team.
I am incredibly grateful for the energy you have put into our work.
It's an honour to join the long and distinguished list of your former PhD students.

The stalwart of the group, James Bennett, has been far more than just a supervisor, but also a patient sounding board, a guide to the light when no model will converge, and a great friend.
I hope I didn't bother you too much, but to work so closely with you over the past years has been a pleasure.
My supervisor, Seth Flaxman, has been a fountain of ideas and energy, and every conversation has stretched my thinking.
Robbie Parks and Kyle Foreman have looked out for me throughout the past years and I'd like to thank them for pushing me towards new opportunities whenever they can.

I am part of an incredibly talented and welcoming group of researchers at Imperial.
Ricky Nathvani, Sierra Clark, Honor Bixby, Perviz Asaria, Bin Zhou, Jonny Pearson-Stuttard, Vasilis Kontis, and the wider group of NCD-RisC collaborators have provided a constant stream of insights and entertainment.
My fellow PhD students, Barbara Metzler, Emily Muller, and Victor Lhoste, have survived the journey with me and made the experience so much fun.
Beyond the group, I'd like to thank Adam Howes for helpful, technical conversations and Sam Acors for unhelpful, non-technical conversations.
There would be no results in this thesis without the dedicated IT support from Eric Johnson and the invaluable probabilistic modelling advice from the oracle-like Chris Paciorek.

Thank you to my mother, Claire, and to my father, Aly, for my incredible upbringing and the foundation you have laid for me.
Thanks to Rosalind as well.
Of everyone, my biggest thanks go to Solange for keeping me sane, happy and loved throughout.
I am very lucky to have you.

This thesis is dedicated to my grandfather, Geoff Hardern, who sadly passed during my PhD studies.
It was his dream for all of his grandchildren to go to university, and I hope he'd be proud of how long I have spent there.